---
title: "Property Value in USD MI data April 2018"
output: html_notebook

---

Based on MI data at this page http://data.miningintelligence.com/property/browsesearch.aspx?vt=84&st=ResorValTotDesc

Get the property values and the property details table. 


 
```{r}

library(readr)
library(tidyverse)


properties_resource_value <- read_csv("C:/Users/Admin/Downloads/properties-resources value-report-michael-mccrae-20180406121215.csv")
View(properties_resources_value_report_michael_mccrae_20180406121215)

properties_overview <- read_csv("C:/Users/Admin/Downloads/properties-overview-report-michael-mccrae-20180406193139.csv")
View(properties_overview_report_michael_mccrae_20180406122417)

properties_ownership <- read_csv("C:/Users/Admin/Downloads/properties-ownership-report-michael-mccrae-20180406193302.csv")

head(properties_resource_value)

head(properties_overview)

head(properties_ownership)

```
 
 Let's try charting just the properties resource value
 
 
```{r}

prv <- properties_resource_value %>% select(Property, TotalValueBUSD) %>% filter(TotalValueBUSD>20000) %>% arrange(desc(TotalValueBUSD))

prv


```


How about a count by Primary Commodity? 

```{r}

prv3 <- properties_resource_value %>% group_by(PrimaryCommodity) %>% count()

prv3


```





K. Let's chart

```{r}

ggplot(prv, aes(x=reorder(Property,TotalValueBUSD), y=TotalValueBUSD)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=TotalValueBUSD))+
  coord_flip() 


```


Facet by commodity

```{r}

prv$PrimaryCommodity <-as.factor(prv$PrimaryCommodity,exclude = NULL)


ggplot(prv, aes(x=reorder(Property,TotalValueBUSD), y=TotalValueBUSD)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=TotalValueBUSD))+
  coord_flip() +
  facet_grid(~PrimaryCommodity)



```







Let's do some joining!

I will make the properties_value primary. 


```{r}

joined_properties_value2 <- properties_value %>% inner_join(properties_overview, by="PropertyID")

View(joined_properties_value2)

```


Let's look at what we got. What's the most valuable. 

```{r}

joined3 <- joined_properties_value2 %>% select(Property.x, Country, PrimaryCommodity, ActivityStatus, TotalValueBUSD) %>% filter(ActivityStatus=="Feasibility") %>% filter(TotalValueBUSD>2000) %>% arrange(desc(TotalValueBUSD))

joined3



```


Now let's do some charts using joined3

```{r}

ggplot(joined3, aes(x=reorder(Property.x,TotalValueBUSD), y=TotalValueBUSD, fill=PrimaryCommodity)) +
  geom_bar(stat="identity") +
  coord_flip()



```



Now let's do some charts using just properties_value



